---
title: " Figs. and  stats. Cold acclimation of mesophyll conductance and leakiness in Miscanthus x giganteus"
author: "Erika Serrano"
date: "12/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE )
```

Loading packages
```{r, loading packages, message=FALSE, warning=FALSE}

options(java.parameters = "-Xmx4g" )
library(XLConnect)
library(doBy)
library(ez)
library(reshape2)
library(scales)
library(plyr)
library(minpack.lm)
library(lmerTest)
library(nlWaldTest)
library(ggplot2)
library(mice)

```


Loading the results from the script "Misc combined C4 and discrimination model.Rmd"
```{r, loading data}
gmsat0<-read.csv("results_gmsat0.csv", head=TRUE)
gmCAlim0<-read.csv("results_gmCAlim.csv", head=TRUE)
gmPPDKlim0<-read.csv("results_gmCA_PPDKlim.csv", head=TRUE)
```

```{r, functions, echo=FALSE}
se<- function(x, ...) {
  se <- sd(x, ...)/sqrt(sum(!is.na(x)))
  return(se)
}


out = function(x,phi) {
  
  # Get Q1 and Q3
  qnt = quantile(x$phi, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  iqt = 1.5 * IQR(x$phi)
  
  
  # Apply on a copy of the original data
 x[x$phi < (qnt[1] - iqt )|x$phi > (qnt[2] + iqt),] = NA
  

  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

outliers<-function(x,phi){
  #Add a unique identifier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, sep="_"))
  x<-ddply(x, .(id),function(x) out(x,phi))
  return(x)
}



out_gbsPa= function(x,gbsPa) {
  
  # Get Q1 and Q3
  
  qnt = quantile(x$gbsPa, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  
  iqt = 1.5 * IQR(x$gbsPa)
  
  
  # Apply on a copy ogbsPa the original data
  
  x[x$gbsPa < (qnt[1] - iqt )|x$gbsPa > (qnt[2] + iqt),] = NA
  
  
  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

outliers_gbsPa<-function(x,gbsPa){
  #Add a unique identigbsPaier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, sep="_"))
  x<-ddply(x, .(id),function(x) out_gbsPa(x,gbsPa))
  return(x)
}

out_gmPa = function(x,gmPa) {
  
  # Get Q1 and Q3
  
  qnt = quantile(x$gmPa, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  
  iqt = 1.5 * IQR(x$gmPa)
  
  
  # Apply on a copy ogmPa the original data
  
  x[x$gmPa < (qnt[1] - iqt )|x$gmPa > (qnt[2] + iqt),] = NA
  
  
  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

outliers_gmPa<-function(x,gmPa){
  #Add a unique identigmPaier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, sep="_"))
  x<-ddply(x, .(id),function(x) out_gmPa(x,gmPa))
  return(x)
}

out_Cbs= function(x,Cbs) {
  
  # Get Q1 and Q3
  
  qnt = quantile(x$Cbs, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  
  iqt = 1.5 * IQR(x$Cbs)
  
  
  # Apply on a copy oCbs the original data
  
  x[x$Cbs < (qnt[1] - iqt )|x$Cbs > (qnt[2] + iqt),] = NA
  
  
  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

outliers_Cbs<-function(x,Cbs){
  #Add a unique identiCbsier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, sep="_"))
  x<-ddply(x, .(id),function(x) out_Cbs(x,Cbs))
  return(x)
}

out_Cm = function(x,Cm) {
  
  # Get Q1 and Q3
  
  qnt = quantile(x$Cm, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  
  iqt = 1.5 * IQR(x$Cm)
  
  
  # Apply on a copy oCm the original data
  
  x[x$Cm < (qnt[1] - iqt )|x$Cm > (qnt[2] + iqt),] = NA
  
  
  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

outliers_Cm<-function(x,Cm){
  #Add a unique identiCmier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, sep="_"))
  x<-ddply(x, .(id),function(x) out_Cm(x,Cm))
  return(x)
}

out_KCA = function(x,KCAmax) {
  
  # Get Q1 and Q3
  qnt = quantile(x$KCAmax, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  iqt = 1.5 * IQR(x$KCAmax)
  
  
  # Apply on a copy of the original data
  x[x$KCAmax < (qnt[1] - iqt )|x$KCAmax > (qnt[2] + iqt),] = NA
  
  
  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

out_leak_SvC_2014= function(x,leak_SvC_2014) {
  
  # Get Q1 and Q3
  
  qnt = quantile(x$leak_SvC_2014, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  
  iqt = 1.5 * IQR(x$leak_SvC_2014)
  
  
  # Apply on a copy oCm the original data
  
  x[x$leak_SvC_2014 < (qnt[1] - iqt )|x$leak_SvC_2014 > (qnt[2] + iqt),] = NA
  
  
  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

outliers_leak_SvC_2014<-function(x,leak_SvC_2014){
  #Add a unique identiCmier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, sep="_"))
  x<-ddply(x, .(id),function(x) out_leak_SvC_2014(x,leak_SvC_2014))
  return(x)
}

out_vp= function(x,Vp_SvC_2014) {
  
  # Get Q1 and Q3
  
  qnt = quantile(x$Vp_SvC_2014, probs=c(.25, .75))
  
  # Get the interquartile range time 1.5
  
  iqt = 1.5 * IQR(x$Vp_SvC_2014)
  
  # Apply on a copy oCm the original data
  
  x[x$Vp_SvC_2014 < (qnt[1] - iqt )|x$Vp_SvC_2014 > (qnt[2] + iqt),] = NA
  
  # Remove incomplete cases and return the resulted variables
  return(x[complete.cases(x),])
}

outliers_vp<-function(x,Vp_SvC_2014){
  #Add a unique identifier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, sep="_"))
  x<-ddply(x, .(id),function(x) out_vp(x,Vp_SvC_2014))
  return(x)
}


```

Calculates r~LIGHT~ from the *A*~Ci~ curves

```{r, RLIGHT functions}
#This function finds the slope s´and the intercept r light for the initial portion of a light curve
r_light1<-function(x){
  #x$PARYII3<-(x$PARi*x$PhiPS2.mean)/3
  x$PARYII3<-(x$PARi*x$PhiPS2)/3
  
  #m<-(lm(Photo.mean~PARYII3, data=x))
  m<-(lm(Photo~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  if (intercept<0) x<-subset(x,x$Point %in% c("50","75","125"))
  
  m<-(lm(Photo~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  
  if (intercept<0) x<-subset(x,x$Point %in% c("50","75"))
  m<-(lm(Photo~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  
  #This code extracts the slope from model m and rename it slope instead of Ci_Pa 
  x$rlight<-(-1)*unname(coefficients(m)[1])
  x$s<-unname(coefficients(m)[2])
  return(x)}

#Plotting the Aci curves with the initial slope of 4 points model by a straigh line
hidden_rlight1<- function(x, xlim = NULL, ylim = NULL)
{ 
  x$PARYII3<-(x$PARi*x$PhiPS2)/3
  
  if (is.null(ylim)) 
    ylim <- with(x, c(min(-5), 1.1 * max(Photo)))
  if (is.null(xlim)) 
    xlim <- with(x, c(0, max(PARYII3)))
  
  m<-(lm(Photo~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  if (intercept<0) x<-subset(x,x$Point %in% c("50","75","125"))
  
  m<-(lm(Photo~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  
  if (intercept<0) x<-subset(x,x$Point %in% c("50","75"))
  m<-(lm(Photo~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  
  
  x<-x[order(x$Photo),]#Organize in order to Photo values so the initial slope are the first points
  
  with(x, plot(PARYII3, Photo, type = "n", ylim = ylim, xlim = c(0,80), xaxs ="i", main = levels(as.factor(x$id)),
               #text(labels = as.character(x[,"Point"]), pos = 4),
               xlab = expression(italic(PARYII3) ~ ~(mu * mol~ m^-2 ~ s^-1)), 
               ylab = expression(italic(A)[net] ~ ~(mu * mol ~ m^-2 ~ s^-1), side=-2)))
  with(x, points(PARYII3, Photo, pch = 19,cex=2, col= "forestgreen"))
  
  #with(x, arrows(PARYII3,Photo + Photo.se, PARYII3,
                 #Photo - Photo.se,code=3,angle=90,len=0.03))
  p<- seq(-10,160,1)
  with(x, points(p,predict(m, list(PARYII3=p)) , type = "l", col = "blue", 
                 lwd = 2))
  
  legend(x="bottomright",legend=paste(" Rlight intercept",as.character(round(intercept,3)),sep = " "))
  return(x)
}

#Plotting all the Aci curves in a pdf file
plot_rlight1<-function(x){
  
  #Add a unique identifier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp,x$plant, x$Oxygen.,sep="_"))
  #Summary based on this identifier 
  x<-summaryBy(.~ id+GrowthTemp+temp+plant+Point+Oxygen., data=x, keep.names = T,FUN = c(mean))
  
  pdf("rlight_plots_byplant.pdf")
  dlply(x, .(id),function(x) hidden_rlight1(x))
  #dev.off()
  is<-ddply(x, .(id),function(x) r_light1(x))
  x<-merge(x,is)
  
  return(x)}

### This code is when I am working with the mean of plants it has the .mean 
#This function finds the initial slope using the first 4 points in an Aci curve
r_light<-function(x){
  #x$PARYII3<-(x$PARi*x$PhiPS2.mean)/3
  x$PARYII3<-(x$PARi.mean*x$PhiPS2.mean)/3
  
  #m<-(lm(Photo.mean~PARYII3, data=x))
  m<-(lm(Photo.mean~PARYII3, data=x))
  
  #This code extracts the slope from model m and rename it slope instead of Ci_Pa 
  x$rlight<-(-1)*unname(coefficients(m)[1])
  x$s<-unname(coefficients(m)[2])
  return(x)}

#Plotting the Aci curves with the initial slope of 4 points model by a straigh line
hidden_rlight<- function(x, xlim = NULL, ylim = NULL)
{ 
  x$PARYII3<-(x$PARi.mean*x$PhiPS2.mean)/3
  
  if (is.null(ylim)) 
    ylim <- with(x, c(min(-5), 1.1 * max(Photo.mean)))
  if (is.null(xlim)) 
    xlim <- with(x, c(0, max(PARYII3)))
  
  m<-(lm(Photo.mean~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  if (intercept<0) x<-subset(x,x$Point %in% c("50","75","125"))
  
  m<-(lm(Photo.mean~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  
  if (intercept<0) x<-subset(x,x$Point %in% c("50","75"))
  m<-(lm(Photo.mean~PARYII3, data=x))
  intercept<-(-1)*coef(m)[1]
  
  
  x<-x[order(x$Photo.mean),]#Organize in order to Photo values so the initial slope are the first points
  
  with(x, plot(PARYII3, Photo.mean, type = "n", ylim = ylim, xlim = c(0,80), xaxs ="i", main = levels(as.factor(x$id)),
               #text(labels = as.character(x[,"Point"]), pos = 4),
               xlab = expression(italic(PARYII3) ~ ~(mu * mol~ m^-2 ~ s^-1)), 
               ylab = expression(italic(A)[net] ~ ~(mu * mol ~ m^-2 ~ s^-1), side=-2)))
  with(x, points(PARYII3, Photo.mean, pch = 19,cex=2, col= "forestgreen"))
  
  #with(x, arrows(PARYII3,Photo + Photo.se, PARYII3,
  #Photo - Photo.se,code=3,angle=90,len=0.03))
  p<- seq(-10,160,1)
  with(x, points(p,predict(m, list(PARYII3=p)) , type = "l", col = "blue", 
                 lwd = 2))
  
  legend(x="bottomright",legend=paste(" Rlight intercept",as.character(round(intercept,3)),sep = " "))
  return(x)
}


#Plotting all the Aci curves in a pdf file
plot_rlight<-function(x){
  
  #Add a unique identifier that includes GrowthTemp, measurement temp and plant
  x$id<-as.character(paste(x$GrowthTemp, x$temp, x$plant, x$Oxygen.,sep="_"))
  #Summary based on this identifier 
  x<-summaryBy(.~ id+GrowthTemp+plant+temp+Point+Oxygen., data=x, keep.names = T,FUN = c(mean))
  
  pdf("rlight_plots_by temp.pdf")
  dlply(x, .(id),function(x) hidden_rlight(x))
  #dev.off()
  is<-ddply(x, .(id),function(x) r_light(x))
  x<-merge(x,is)
  
  return(x)}

```
$\phi$ and *V*~p~ for von Caemmerer et al. (2014)

```{r, leakiness and Vp for von Caemmerer et al. (2014)}
b3p_SvC_2014 <- with(data = gmPPDKlim0, b3p-(e*(Rlight/(Photo+Rlight)-0.5*Rlight/(Photo+0.5*Rlight))))
b4p_SvC_2014 <- with(data = gmPPDKlim0, gmPPDKlim0$b4p-(e*0.5*Rlight/(Photo+0.5*Rlight)))

phi_num_SvC_2014 <- with(data = gmPPDKlim0, (( ((1-t)/(1+t))*Dobs ) - (a_bar_Ci/(1+t)) - (1.8-b4p_SvC_2014)*(Photo/(1000000000000*CaPa)) - (b4p_SvC_2014-(a_bar_Ci/(1+t)) )*(Ci.Ca)))
phi_deno_SvC_2014 <- with(data = gmPPDKlim0, (b3p_SvC_2014 - 1.8) * (Ci.Ca-(Photo/(CaPa*1000000000000))) )

gmPPDKlim0$phi_SvC_2014 <- phi_num_SvC_2014/phi_deno_SvC_2014 #Leakiness

gmPPDKlim0$Vp_SvC_2014 = with(data = gmPPDKlim0,(Photo+0.5*Rlight)/(1-phi_SvC_2014)) # Vp for von Caemmerer 2014

```

Removing outliers from the dataset
```{r, removing outliers from the dataset, eval= TRUE, echo=FALSE}
gmsat1 <- gmsat0[c(gmsat0$Dobs>0 & gmsat0$Cbs>0 & gmsat0$gbsPa>0 & gmsat0$Cm>0 & gmsat0$Cm < gmsat0$CiPa & gmsat0$phi>0 & gmsat0$phi<1 & gmsat0$Sum.diff<0.5),]
gmCAlim1 <- gmCAlim0[c(gmCAlim0$Dobs>0 & gmCAlim0$Cbs>0 & gmCAlim0$gbsPa>0 & gmCAlim0$Cm>0 & gmCAlim0$Cm < gmCAlim0$CiPa & gmCAlim0$phi>0 & gmCAlim0$phi<1 & gmCAlim0$Sum.diff<0.5),]
gmPPDKlim1 <- gmPPDKlim0[c(gmPPDKlim0$Dobs>0 & gmPPDKlim0$Cbs>0 & gmPPDKlim0$gbsPa>0 & gmPPDKlim0$Cm>0 & gmPPDKlim0$Cm < gmPPDKlim0$CiPa & gmPPDKlim0$phi>0 & gmPPDKlim0$phi<1 & gmPPDKlim0$phi_SvC_2014<1 & gmPPDKlim0$Sum.diff< 0.5),]

gmsat1 <- outliers_gbsPa(gmsat1,gbsPa)
gmsat1 <- outliers_Cbs(gmsat1,Cbs)
gmsat1 <- outliers_Cm(gmsat1,Cm)
gmsat1 <- outliers(gmsat1,phi)
gmsat1 <- outliers_gmPa(gmsat1,gmPa)

boxplot(gmPa~temp*GrowthTemp, data=gmsat1)
boxplot(gmPa~temp*GrowthTemp, data=gmsat1)
boxplot(phi~temp*GrowthTemp, data=gmsat1)
boxplot(gbsPa~temp*GrowthTemp, data=gmsat1)
boxplot(Cbs~temp*GrowthTemp, data=gmsat1)

gmCAlim1 <- outliers_gbsPa(gmCAlim1,gbsPa)
gmCAlim1 <- outliers_Cbs(gmCAlim1,Cbs)
gmCAlim1 <- outliers_Cm(gmCAlim1,Cm)
gmCAlim1 <- outliers(gmCAlim1,phi)
gmCAlim1 <- outliers_gmPa(gmCAlim1,gmPa)
boxplot(gmPa~temp*GrowthTemp, data=gmCAlim1)
boxplot(phi~temp*GrowthTemp, data=gmCAlim1)
boxplot(gbsPa~temp*GrowthTemp, data=gmCAlim1)

gmPPDKlim1 <- outliers_gbsPa(gmPPDKlim1,gbsPa)
gmPPDKlim1 <- outliers_Cbs(gmPPDKlim1,Cbs)
gmPPDKlim1 <- outliers_Cm(gmPPDKlim1,Cm)
gmPPDKlim1 <- outliers(gmPPDKlim1,phi)
gmPPDKlim1 <- outliers_gmPa(gmPPDKlim1,gmPa)

boxplot(gmPa~temp*GrowthTemp, data=gmPPDKlim1)
boxplot(phi~temp*GrowthTemp, data=gmPPDKlim1)
boxplot(gbsPa~temp*GrowthTemp, data=gmPPDKlim1)
boxplot(Photo~temp*GrowthTemp, data=gmPPDKlim1)
boxplot(phi_SvC_2014~temp*GrowthTemp, data=gmPPDKlim1)


gm1 <- summaryBy(.~ id+plant+GrowthTemp, data=gmsat1, keep.names = T)
gm2 <- summaryBy(.~ id+plant+GrowthTemp, data=gmCAlim1, keep.names = T)
gm3 <- summaryBy(.~ id+plant+GrowthTemp, data=gmPPDKlim1, keep.names = T)

write.csv(gm1,file = "gm1_Nerea_April2019c.csv", row.names = FALSE)
write.csv(gm2,file = "gm2_Nerea_April2019c.csv", row.names = FALSE)
write.csv(gm3,file = "gm3_Nerea_April2019c.csv", row.names = FALSE)

```

Here leakiness is calculated following von Caemmerer 2014 as



$$ \phi = \frac { (1-t)  ∆_{obs} \frac{  \overline{ a_{Ci} }   }{(1+t)} - (a_w - b_4) . \frac{A_{net} }{g_m.C_a}-(b_4 - \frac{   \overline{ a_{Ci} }     }{ (1+t) }).\frac{C_i}{C_a} } { (b_3  - s) . (\frac{C_i}{C_a} - \frac{A_{net} }{g_m.C_a})  } $$

### CA~sat~ model

Imputation of missing points
```{r reads data for the CA~sat ~ model, eval=TRUE, warning = FALSE, echo= FALSE}

gm1<-read.csv( "gm1_Nerea_April2019c.csv", head=TRUE)
avg_gm1a<- summaryBy(phi~ GrowthTemp+temp+plant, data=gm1, keep.names = T, na.rm= TRUE)
ezDesign(data = avg_gm1a,
         temp,
         plant,
         GrowthTemp)

avg_gm1a <- reshape(avg_gm1a, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")
invisible(imputed_Data <- mice(avg_gm1a,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
comp_f <- mice::complete(imputed_Data,1)
colnames(comp_f) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
f1 <- melt(comp_f,id=c("GrowthTemp","plant"))
colnames(f1) <- c("GrowthTemp","plant","temp","phi")


# Loading data for gmPa
avg_gm1c<- summaryBy(gmPa~ GrowthTemp+temp+plant, data=gm1, keep.names = T, na.rm= TRUE)
avg_gm1c <- reshape(avg_gm1c, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm1c,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
gmPa1 <-  mice::complete(imputed_Data,1)
colnames(gmPa1) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
gmPa1 <- melt(gmPa1,id=c("GrowthTemp","plant"))
colnames(gmPa1) <- c("GrowthTemp","plant","temp","gmPa")


avg_gmm1 <- merge(gmPa1, f1, by=c("GrowthTemp","plant","temp"))

# Loading data for gbsPa
avg_gm1d<- summaryBy(gbsPa ~ GrowthTemp + temp + plant, data=gm1, keep.names = T, na.rm= TRUE)
avg_gm1d <- reshape(avg_gm1d, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm1d,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
gbsPa1 <-  mice::complete(imputed_Data,1)
colnames(gbsPa1) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
gbsPa1 <- melt(gbsPa1,id=c("GrowthTemp","plant"))
colnames(gbsPa1) <- c("GrowthTemp","plant","temp","gbsPa")



gbsPagm1 <- merge(gbsPa1, avg_gmm1, by=c("GrowthTemp","plant","temp")) # merges imputed data

gm1 <- gm1[,!(colnames(gm1) %in% c("gbsPa", "gmPa", "phi"))]
gm1 <- merge(gm1, gbsPagm1, by=c("GrowthTemp","plant","temp"),all = TRUE) #creates full dataset with imputed columns



ezDesign(data = gm1,
         temp,
         plant,
         GrowthTemp)

gm1$method<- rep("sat",112)
write.csv(gm1,file = "gm1_Nerea_April2019 imputedc.csv", row.names = FALSE)
```

### CA~lim~ model

Imputation of missing points
```{r reads data for the CA~lim~ model, eval=TRUE, warning = FALSE, echo = FALSE}

# gm CAlim
gm2<-read.csv("gm2_Nerea_April2019c.csv", head=TRUE)
avg_gm2al<- summaryBy(phi~ GrowthTemp+temp+plant, data=gm2, keep.names = T, na.rm= TRUE)
ezDesign(data = avg_gm2al,
         temp,
         plant,
         GrowthTemp)

avg_gm2al <- reshape(avg_gm2al, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")
invisible(imputed_Data <- mice(avg_gm2al,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
comp_f <-  mice::complete(imputed_Data,1)
colnames(comp_f) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
f2 <- melt(comp_f,id=c("GrowthTemp","plant"))
colnames(f2) <- c("GrowthTemp","plant","temp","phi")


# Loading data for gmPa
avg_gm2c<- summaryBy(gmPa~ GrowthTemp+temp+plant, data=gm2, keep.names = T, na.rm= TRUE)
avg_gm2c <- reshape(avg_gm2c, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm2c,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
gmPa2 <-  mice::complete(imputed_Data,1)
colnames(gmPa2) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
gmPa2 <- melt(gmPa2,id=c("GrowthTemp","plant"))
colnames(gmPa2) <- c("GrowthTemp","plant","temp","gmPa")


avg_gmm2 <- merge(gmPa2, f2, by=c("GrowthTemp","plant","temp"))

# Loading data for gbsPa
avg_gm2d<- summaryBy(gbsPa~ GrowthTemp+temp+plant, data=gm2, keep.names = T, na.rm= TRUE)
avg_gm2d <- reshape(avg_gm2d, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm2d,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
gbsPa2 <-  mice::complete(imputed_Data,1)
colnames(gbsPa2) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
gbsPa2 <- melt(gbsPa2,id=c("GrowthTemp","plant"))
colnames(gbsPa2) <- c("GrowthTemp","plant","temp","gbsPa")


gbsPagm2 <- merge(gbsPa2, avg_gmm2, by=c("GrowthTemp","plant","temp"))


gm2 <- gm2[,!(colnames(gm2) %in% c("gbsPa", "gmPa", "phi"))]
gm2 <- merge(gm2, gbsPagm2, by=c("GrowthTemp","plant","temp"),all = TRUE)


ezDesign(data = gm2,
         temp,
         plant,
         GrowthTemp)

gm2$method<- rep("CAlim",112)
write.csv(gm2,file = "gm2_Nerea_April2019 imputedc.csv", row.names = FALSE)
```

#CA and PPDK lim model

Imputation of missing points
```{r, reads data for the CA+PPDK~lim~ model, eval=TRUE, warning = FALSE, echo=FALSE}

gm3<-read.csv("gm3_Nerea_April2019c.csv", head=TRUE)
avg_gm3al<- summaryBy(phi~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
ezDesign(data = avg_gm3al,
         temp,
         plant,
         GrowthTemp)

avg_gm3al <- reshape(avg_gm3al, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")
invisible(imputed_Data <- mice(avg_gm3al,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
comp_f <-  mice::complete(imputed_Data,1)
colnames(comp_f) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
f3 <- melt(comp_f,id=c("GrowthTemp","plant"))
colnames(f3) <- c("GrowthTemp","plant","temp","phi")

# Loading data for phi. inf.comp
avg_gm3bl<- summaryBy(phi_SvC_2014~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3bl <- reshape(avg_gm3bl, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3bl,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
comp_inf <-  mice::complete(imputed_Data,1)
colnames(comp_inf) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
inf3 <- melt(comp_inf,id=c("GrowthTemp","plant"))
colnames(inf3) <- c("GrowthTemp","plant","temp","phi_SvC_2014")

#finf3 <- merge(f3, inf3, by=c("GrowthTemp","plant", "temp"))
f3inf3 <- merge(f3, inf3, by=c("GrowthTemp","plant", "temp"))


# Loading data for gmPa
avg_gm3c<- summaryBy(gmPa~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3c <- reshape(avg_gm3c, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3c, m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
gmPa3 <-  mice::complete(imputed_Data,1)
colnames(gmPa3) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
gmPa3 <- melt(gmPa3,id=c("GrowthTemp","plant"))
colnames(gmPa3) <- c("GrowthTemp","plant","temp","gmPa")

avg_gmm3 <- merge(gmPa3, f3inf3, by=c("GrowthTemp","plant","temp"))


# Loading data for gbsPa
avg_gm3d<- summaryBy(gbsPa~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3d <- reshape(avg_gm3d, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3d,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
gbsPa3 <-  mice::complete(imputed_Data,1)
colnames(gbsPa3) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
gbsPa3 <- melt(gbsPa3,id=c("GrowthTemp","plant"))
colnames(gbsPa3) <- c("GrowthTemp","plant","temp","gbsPa")

gbsPagm3 <- merge(gbsPa3, avg_gmm3, by=c("GrowthTemp","plant","temp"))


# Loading data for Photo
avg_gm3e<- summaryBy(Photo~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3e <- reshape(avg_gm3e, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3e,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
Photo3 <-  mice::complete(imputed_Data,1)
colnames(Photo3) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
Photo3 <- melt(Photo3,id=c("GrowthTemp","plant"))
colnames(Photo3) <- c("GrowthTemp","plant","temp","Photo")

m3e <- merge(gbsPagm3, Photo3, by=c("GrowthTemp","plant","temp"))


# Loading data for Cond
gm3$Cond<- gm3$Cond*1000/gm3$Press

avg_gm3f<- summaryBy(Cond~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3f <- reshape(avg_gm3f, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3f,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
Cond3 <-  mice::complete(imputed_Data,1)
colnames(Cond3) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
Cond3 <- melt(Cond3,id=c("GrowthTemp","plant"))
colnames(Cond3) <- c("GrowthTemp","plant","temp","Cond")

m3f <- merge(m3e, Cond3, by=c("GrowthTemp","plant","temp"))


# Loading data for Ci.Ca
avg_gm3g<- summaryBy(Ci.Ca~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3g <- reshape(avg_gm3g, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3g,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
Ci.Ca3 <-  mice::complete(imputed_Data,1)
colnames(Ci.Ca3) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
Ci.Ca3 <- melt(Ci.Ca3,id=c("GrowthTemp","plant"))
colnames(Ci.Ca3) <- c("GrowthTemp","plant","temp","Ci.Ca")

m3g <- merge(m3f, Ci.Ca3, by=c("GrowthTemp","plant","temp"))


# Loading data for Dobs
avg_gm3h<- summaryBy(Dobs~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3h <- reshape(avg_gm3h, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3h,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
Dobs3 <-  mice::complete(imputed_Data,1)
colnames(Dobs3) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
Dobs3 <- melt(Dobs3,id=c("GrowthTemp","plant"))
colnames(Dobs3) <- c("GrowthTemp","plant","temp","Dobs")

m3h <- merge(m3g, Dobs3, by=c("GrowthTemp","plant","temp"))

# Loading data for vp
avg_gm3i<- summaryBy(Vp_SvC_2014~ GrowthTemp+temp+plant, data=gm3, keep.names = T, na.rm= TRUE)
avg_gm3i <- reshape(avg_gm3i, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_gm3i,m=5, maxit=50, metiod= 'pmm', seed =500))
invisible (summary(imputed_Data))
Vp_SvC_2014 <-  mice::complete(imputed_Data,1)
colnames(Vp_SvC_2014) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
Vp_SvC_2014 <- melt(Vp_SvC_2014,id=c("GrowthTemp","plant"))
colnames(Vp_SvC_2014) <- c("GrowthTemp","plant","temp","vp_SvC_2014")

m3i <- merge(m3h, Vp_SvC_2014, by = c("GrowthTemp","plant","temp"))


#____________________    calculating rlight from the Aci curves dataset   ___________________________________
rlight<-read.csv("Rlightsubset Misc.csv")
rlight<-plot_rlight1(rlight)
rlight<-rlight[!rlight$rlight<0,]

# Loading data for R_LIGHT
avg_rlight<- summaryBy(rlight~ GrowthTemp+temp+plant, data=rlight, keep.names = T, na.rm= TRUE)
avg_rlight <- reshape(avg_rlight, idvar= c("GrowthTemp","plant"),timevar = "temp" ,direction = "wide")

invisible(imputed_Data <- mice(avg_rlight,m=5, maxit=50, method= 'pmm', seed =500))
invisible (summary(imputed_Data))
rlight <-  mice::complete(imputed_Data,1)
colnames(rlight) <- c("GrowthTemp","plant","10","15","20","25","30","35","40")
rlight <- melt(rlight,id=c("GrowthTemp","plant"))
colnames(rlight) <- c("GrowthTemp","plant","temp","rlight")
rlight$temp <- as.integer(as.character(rlight$temp))

## now take mean and error for plotting 
meanse_rlight<- summaryBy(rlight~ GrowthTemp+temp, data=rlight,FUN = c(mean,se))
colnames(meanse_rlight) <- c("GrowthTemp","temp","rlight", "rlight.se")

m3_rlight <- merge(m3i, meanse_rlight)


gm3 <- gm3[,!(colnames(gm3) %in% c("gbsPa", "gmPa", "phi", "phi_SvC_2014", "Photo", "Cond", "Ci.Ca", "Dobs","vp_SvC_2014", "Rlight"))]

gm3<- merge(gm3, m3_rlight, by=c("GrowthTemp","plant","temp"),all = TRUE)

ezDesign(data = gm3,
         temp,
         plant,
         GrowthTemp)

gm3$method<- rep("PPDKlim",112)
write.csv(gm3,file = "gm3_Nerea_April2019 imputedc.csv", row.names = FALSE)
```



This is the imputed dataset for resubmission 26 Nov 2019

```{r, imputed dataset for Misc paper}

gm1<-read.csv("gm1_Nerea_April2019 imputedc.csv", head=TRUE)
gm2<-read.csv("gm2_Nerea_April2019 imputedc.csv", head=TRUE)
gm3<-read.csv("gm3_Nerea_April2019 imputedc.csv", head=TRUE)

```

Calculating A~sat~ from the A~Ci~ curves dataset

```{r, cleaning Aci curves, echo = FALSE}
x<-read.csv("AciMisc.csv")##read dataframe
x$id<-as.character(paste(x$GrowthTemp, x$temp, x$plant,sep="_"))

# Removing plants that do not have more than one point at 200

x<-x[!c(x$id=="14C_10_plant3" & x$Obs %in% c(15,16)) ,]
x<-x[!c(x$id=="14C_20_plant1") ,]
x<-x[!c(x$id=="14C_35_plant1") ,]

#Removing plants that are non-sensical in all the points
x<-x[!c(x$id=="14C_10_plant5") ,]
x<-x[!c(x$id=="14C_10_plant2" & x$Obs %in% c(314,318,320,322,323,328,329,330)) ,]

#Removing points that produce negative slope
x<-x[!c(x$id=="25C_15_plant2" & x$Obs %in% c(137)) ,]

#Removing plants that have the extra 380 point or an isolated estrange point
x<-x[!c(x$id=="14C_10_plant4" & x$Obs %in% c(37,38)) ,]
x<-x[!c(x$id=="14C_15_plant2" & x$Obs %in% c(118)) ,]
x<-x[!c(x$id=="14C_15_plant5" & x$Obs %in% c(111)) ,]
x<-x[!c(x$id=="14C_35_plant3" & x$Obs %in% c(189,190)) ,]
x<-x[!c(x$id=="14C_40_plant2" & x$Obs %in% c(116)) ,]
x<-x[!c(x$id=="25C_10_plant1" & x$Obs %in% c(2)) ,]
x<-x[!c(x$id=="25C_15_plant1" & x$Obs %in% c(140)) ,]
x<-x[!c(x$id=="25C_15_plant3" & x$Obs %in% c(106)) ,]
x<-x[!c(x$id=="25C_15_plant4" & x$Obs %in% c(89)) ,]
x<-x[!c(x$id=="25C_15_plant5" & x$Obs %in% c(173)) ,]
x<-x[!c(x$id=="25C_20_plant1" & x$Obs %in% c(24)) ,]
x<-x[!c(x$id=="25C_20_plant12" & x$Obs %in% c(107)) ,]
x<-x[!c(x$id=="25C_25_plant4" & x$Obs %in% c(107)) ,]

# 18 Oct 2019 Asaph requested the Aci curves
meanse_Aci<- summaryBy( .~ GrowthTemp+temp + Point,data=x,FUN = c(mean, se), na.rm =TRUE)

write.csv(meanse_Aci,file = "Aci curves by GrowthTemp.csv", row.names = FALSE)
```

Creates dataset summarized by plant
```{r, creates dataset summarized by plant}
library(lattice)
meanse1<- summaryBy( Photo + Cond + Ci.Ca + Rlight + Dobs + phi + gbsPa + Cm + gmPa + Cbs + Vp + Sum.diff ~ GrowthTemp+temp,
                     data = gm1, FUN = c(mean, se), na.rm =TRUE)

meanse2<- summaryBy( Photo+ Cond + Ci.Ca + Rlight + Dobs + phi  + gbsPa + Cm + gmPa + Cbs + Vp + Sum.diff~GrowthTemp+temp,
                    data = gm2,FUN = c(mean, se), na.rm =TRUE)

meanse3<- summaryBy( Photo+ Cond + Ci.Ca + rlight + Dobs + phi + phi_SvC_2014 + gbsPa + Cm + gmPa + Cbs + Vpr  + Vp_app + Vp + Vp_SvC_2014+ Sum.diff ~ 
                       GrowthTemp+temp, data=gm3,FUN = c(mean, se), na.rm =TRUE)

write.csv(meanse3,"meanse3 misc v2.csv", row.names = FALSE)
```


This function specifies Miscanthus x giganteous grown at 14°C (open symbols) and 25°C (closed symbols)

```{r, specifies color, eval = TRUE}
COL<- function(meanse3){ifelse(meanse3$GrowthTemp=="14C", "white", "black")} 
CEX=1   ##define size of points

```

Figure 1.  Code to get confidence intervals for A~net~
```{r, rlight functions, echo= TRUE}
arrh_mod<-function(x,Ea,dS,k25,Hd){
  R<- 0.008317 ## unit for KJ per mol per K
  #Hd<- 200
  Tk<- x+273.15
  A<- exp ( Ea*(Tk-298.15)/(298.15*R*Tk) )
  B<- 1+exp(((298.15*dS)-Hd)/(298.15*R))
  C<- 1+exp(((Tk*dS)-Hd)/(Tk*R))
  D<- B/C
  k25*A*D
}


arrh_T<-function(temp,Ea=63.8,dS=1.2,k25= 3.7295521, Hd=366.8){
  R<- 0.008317 ## unit for KJ per mol per K
  #Hd<- 200
  Tk<- temp+273.15
  A<- exp ( Ea*(Tk-298.15)/(298.15*R*Tk) )
  B<- 1+exp(((298.15*dS)-Hd)/(298.15*R))
  C<- 1+exp(((Tk*dS)-Hd)/(Tk*R))
  D<- B/C
  yval<- k25*A*D
  df<- data.frame(yval= yval, temp= temp, Ea=Ea,dS=dS,k25=k25, Hd= Hd)
  return(df)
}
###
fit_arrh25<- function(dat, varnames = list(yval = "Photo", temp = "temp"))
{ 
  arrh_wrap <- function(temp, ...) {
    r <- arrh_T(temp= temp,...)
    r$yval}
  
  nlsfit <- nlsLM(yval ~ arrh_wrap(temp, Ea=Ea,dS=dS,k25=k25, Hd=Hd),data = dat, start = list(Ea= 63.8, dS=1.2, k25=3.7295521, Hd=366.8))
  p <- coef(nlsfit)
  
  arrhrun <- arrh_T(temp = dat$temp,  Ea= p[[1]],  dS = p[[2]], k25= p[[3]], Hd = p[[4]])
  
  arrhrun$Ymeas <- dat$yval
  arrhrun$temp <- dat$temp
  names(arrhrun)[names(arrhrun) == "yval"] <- "Ymodel"
  avars <- match(c("temp", "Ymeas", "Ymodel"), names(arrhrun))
  arrhrun <- arrhrun[, c(avars, setdiff(1:ncol(arrhrun), avars))]
  
  
  l <- list()
  l$df <- arrhrun[order(arrhrun$temp), ]
  l$pars <- summary(nlsfit)$coefficients[, 1:2]
  l$nlsfit <- nlsfit
  formals(arrh_T)$temp<- mean(dat$temp)
  formals(arrh_T)$Ea <- l$pars[1]
  formals(arrh_T)$dS <- l$pars[2]
  formals(arrh_T)$k25 <- l$pars[3]
  formals(arrh_T)$Hd <- l$pars[4]
  l$arrh_T <- arrh_T
  
  class(l)<- "arrhfit"
  return(l)
}


fit_arrh14<- function(dat, varnames = list(yval = "Photo", temp = "temp"))
{ 
  arrh_wrap <- function(temp, ...) {
    r <- arrh_T(temp= temp,...)
    r$yval}
  #Initial values for Vcmax in Lin et al, 2011
  nlsfit <- nlsLM(yval ~ arrh_wrap(temp, Ea=Ea,dS=dS,k25=k25, Hd=Hd),data = dat, start = list(Ea= 63.8, dS=1.2, k25=3.3156579, Hd= 366.8))
            
  p <- coef(nlsfit)
  
  arrhrun <- arrh_T(temp = dat$temp,  Ea= p[[1]],  dS = p[[2]], k25= p[[3]], Hd= p[[4]])
  
  arrhrun$Ymeas <- dat$yval
  arrhrun$temp <- dat$temp
  names(arrhrun)[names(arrhrun) == "yval"] <- "Ymodel"
  avars <- match(c("temp", "Ymeas", "Ymodel"), names(arrhrun))
  arrhrun <- arrhrun[, c(avars, setdiff(1:ncol(arrhrun), avars))]
  
  
  l <- list()
  l$df <- arrhrun[order(arrhrun$temp), ]
  l$pars <- summary(nlsfit)$coefficients[, 1:2]
  l$nlsfit <- nlsfit
  formals(arrh_T)$temp<- mean(dat$temp)
  formals(arrh_T)$Ea <- l$pars[1]
  formals(arrh_T)$dS <- l$pars[2]
  formals(arrh_T)$k25 <- l$pars[3]
  formals(arrh_T)$Hd <- l$pars[4]
  l$arrh_T <- arrh_T
  
  class(l)<- "arrhfit"
  return(l)
}


print.arrhfit <- function (x, ...){
  cat("Result of arrh fit.\n\n")
  cat("Data and predictions:\n")
  print(x$df)
  cat("\nEstimated parameters:\n")
  print(x$pars)
}

#########
bootarrh25<- function(d, nboot=500){
  p <- list()
  for(i in 1:nboot){
    ii <- sample(1:nrow(d), replace=TRUE)
    dat <- d[ii,]
    p[[i]] <- try(fit_arrh25(dat))
    message(i)
  }
  
  q<- p[sapply(p, function(x) class(x) != "try-error")]
  return(q)
}

bootarrh14<- function(d, nboot=500){
  p <- list()
  for(i in 1:nboot){
    ii <- sample(1:nrow(d), replace=TRUE)
    dat <- d[ii,]
    p[[i]] <- try(fit_arrh14(dat))
    message(i)
  }
  
  q<- p[sapply(p, function(x) class(x) != "try-error")]
  return(q)
}

###Function to estimate upper and lower CI
get_CI<- function(b){
  cis <- seq(10, 40, length=100)
  phot <- matrix(ncol=100,nrow=length(b))
  for(i in 1:length(b)){
    phot[i,] <- b[[i]]$arrh_T(temp=cis)$yval
  }
  lcl <- apply(phot,2,quantile, 0.025)
  ucl <- apply(phot,2,quantile, 0.975)
  return(data.frame(Ci=cis, lcl=lcl, ucl=ucl))
}

## Finction to calculate  CI
addpoly<-  function(x,y1,y2,col=alpha("lightgrey",0.8),...){
  ii <- order(x)
  y1 <- y1[ii]
  y2 <- y2[ii]
  x <- x[ii]
  polygon(c(x,rev(x)), c(y1, rev(y2)), col=col, border=NA,...)
}


##################################
##Plotting Function

plot_arrh_ci<- function(dfr, x){
  nadp<- dfr # droplevels(subset(avg_gm, Subtype== "NADP-ME"))
  d1 <- nadp[, c("temp", "GrowthTemp", "Photo")]       ## call what u want from dfr
  names(d1)[c(3)] <- c("yval")        ## redefine the vlue position so they will caryy through out function
  df25<-droplevels(subset(d1, GrowthTemp== "25C"))          ## Subseting dfr for GrowthTemp
  df14<-droplevels(subset(d1, GrowthTemp == "14C"))
  
  mod3<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.7295521, Hd=366.8), data= df25, na.action= "na.omit")
  mod4<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.3156579, Hd=366.8), data= df14, na.action= "na.omit")
  
  anova(mod3,mod4)
  xval<-with(df25, seq(10, 40, length.out= 500))
  
  lines(xval, predict(mod3, newdata = data.frame(temp= xval)),lty= 1, lwd= 2, col= "black")
  lines(xval, predict(mod4, newdata = data.frame(temp= xval)), lty= 2,lwd= 2, col= "black")
  return(c(summary(mod3), summary (mod4)) ) # , coef(mod3), coef(mod4)
}

plot_arrh_ci2<- function(dfr, x){
  nadp<- avg_gm2 # droplevels(subset(avg_gm, Subtype== "NADP-ME"))
  d1 <- nadp[, c("temp", "GrowthTemp", "Photo")]       ## call what u want from dfr
  names(d1)[c(3)] <- c("yval")        ## redefine the vlue position so they will caryy through out function
  df25<-droplevels(subset(d1, GrowthTemp== "25C"))          ## Subseting dfr for GrowthTemp
  df14<-droplevels(subset(d1, GrowthTemp == "14C"))
  
  mod3<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.7295521, Hd=366.8), data= df25, na.action= "na.omit")
  mod4<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.3156579, Hd=366.8), data= df14, na.action= "na.omit")
  
  anova(mod3,mod4)
  xval<-with(df25, seq(10, 40, length.out= 500))
  
  lines(xval, predict(mod3, newdata = data.frame(temp= xval)),lty= 1, lwd= 2, col= "black")
  lines(xval, predict(mod4, newdata = data.frame(temp= xval)), lty= 2,lwd= 2, col= "black")
  return(c(summary(mod3), summary (mod4)) ) # , coef(mod3), coef(mod4)
}

plot_arrh_ci3<- function(dfr, x){
  nadp<- avg_gm3 # droplevels(subset(avg_gm, Subtype== "NADP-ME"))
  d1 <- nadp[, c("temp", "GrowthTemp", "Photo")]       ## call what u want from dfr
  names(d1)[c(3)] <- c("yval")        ## redefine the vlue position so they will caryy through out function
  df25<-droplevels(subset(d1, GrowthTemp== "25C"))          ## Subseting dfr for GrowthTemp
  df14<-droplevels(subset(d1, GrowthTemp == "14C"))
  
  mod3<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.7295521, Hd=366.8), data= df25, na.action= "na.omit")
  mod4<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.3156579, Hd=366.8), data= df14, na.action= "na.omit")
  
  anova(mod3,mod4)
  xval<-with(df25, seq(10, 40, length.out= 500))
  
  lines(xval, predict(mod3, newdata = data.frame(temp= xval)),lty= 1, lwd= 2, col= "black")
  lines(xval, predict(mod4, newdata = data.frame(temp= xval)), lty= 2,lwd= 2, col= "black")
  return(c(summary(mod3), summary (mod4)) ) # , coef(mod3), coef(mod4)
}

plot_arrh_ci4<- function(dfr, x){
  nadp<- avg_gm4 # droplevels(subset(avg_gm, Subtype== "NADP-ME"))
  d1 <- nadp[, c("temp", "GrowthTemp", "Photo")]       ## call what u want from dfr
  names(d1)[c(3)] <- c("yval")        ## redefine the vlue position so they will caryy through out function
  df25<-droplevels(subset(d1, GrowthTemp== "25C"))          ## Subseting dfr for GrowthTemp
  df14<-droplevels(subset(d1, GrowthTemp == "14C"))
  
  mod3<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.7295521, Hd=366.8), data= df25, na.action= "na.omit")
  mod4<- nlsLM(yval ~ arrh_mod(temp,Ea,dS, k25, Hd), start= list(Ea= 63.8, dS=1.2, k25=3.3156579, Hd=366.8), data= df14, na.action= "na.omit")
  
  anova(mod3,mod4)
  xval<-with(df25, seq(10, 40, length.out= 500))
  
  lines(xval, predict(mod3, newdata = data.frame(temp= xval)),lty= 1, lwd= 2, col= "black")
  lines(xval, predict(mod4, newdata = data.frame(temp= xval)), lty= 2,lwd= 2, col= "black")
  return(c(summary(mod3), summary (mod4)) ) # , coef(mod3), coef(mod4)
}


#Temp optimum function 
T_opt <- function (Hd =Hd,dS=dS,Ea=Ea){
  R<-0.0083143 # KiloJules mol-1 K-1
  Topt<- (-Hd) / ((R * log (-Ea/( Ea- Hd))) - dS)
  Topt<- Topt - 273.15
  return (Topt)
}
```




